\LaTeX\ Author Guidelines for ICCV Proceedings

### 2019-05-20 chapters/1_intro.tex
Add Constantin comments

Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient. Despite the fact that there exist a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there has been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g. robustness and efficiency.

@@

In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore in a consistent way its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e. mutual exclusion between clusters. We then theoretically prove that different combinations correspond to existing clustering algorithms as well as new algorithms that we introduce and explore. % The framework can also be easily expended to accommodate additional linkage criteria.
%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec. \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}). At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms. 
%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.

>>>>

Thus, agglomerative clustering algorithms for signed graphs have clear advantages: they are parameter free and efficient. Despite the fact that there exist a variety of these algorithms \cite{keuper2015efficient,levinkov2017comparative,wolf2018mutex,kardoostsolving}, there have been no overarching studies comparing them and making it possible to choose the most appropriate algorithm for particular applications and assess their properties, e.g. robustness and efficiency.

@@

In this paper, we propose a novel theoretical framework for generalizing over agglomerative algorithms for signed graphs by linking them to hierarchical agglomerative clustering, which is a popular bottom-up approach defining an hierarchy of clusters on positive-weighted graphs \cite{lance1967general}. This framework defines an underlying basic algorithm and allows us to explore its combinations with different linkage criteria and \emph{cannot-link constraints}, i.e. mutual exclusion between clusters. We then theoretically prove that different combinations correspond to existing clustering algorithms as well as new algorithms that we introduce and explore. % The framework can also be easily expended to accommodate additional linkage criteria.
%As a first contribution, we reformulate several of these recently proposed graph agglomerative algorithms in a simple review framework (Sec. \ref{sec:general_framework}) that represents a generalization of agglomerative HC to graphs with both attractive and repulsive edge weights (see Figure \ref{fig:intro_figure} for a visual abstract). From this new point of view, agglomerative HC and algorithms proposed in \cite{levinkov2017comparative,wolf2018mutex,lance1967general,kardoostsolving} all share a general procedure but differ in the way inter-cluster interaction is updated after each iteration (Table \ref{tab:linkage-criteria}). At the same time, we also show that this framework allows us to introduce totally new variations of these algorithms. 
%Ultimately, by presenting this simple general approach, our hope is to motivate a deeper understanding of the connection between algorithms for unsigned and signed graphs.

### 2019-05-20 chapters/5_experiments_noise.tex
Add Constantin comments

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
% The poor scores achieved by THRESH highlight the difficulty of the task. 
\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage). The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem. 
In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
Our hypothesis to explain this superior performances it that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error. 
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Arand-Score \\(higher is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
DTWS + \algname{} & Average& \TODO{} \\
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Arand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221}\\
PNI-UNet & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.244 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{2.3em}
    \captionof{table}{Current leaderboard of the CREMI challenge \TODO{Update refs and check}}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

@@

\textbf{Noise experiments } Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework. Additionally, we run a set of experiments where the CNN predictions are perturbed by noise, in order to highlight the properties of each \algname{} algorithm and perform an in-depth comparison that is as quantitative as possible. Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences.  
Fig. \ref{fig:noise_plots} summarize our 12000 noise experiments: we focused on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise, both with and without use of long-range connections in the grid-graph. % In Fig. \ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence. See Fig. \ref{fig:noise_split} in Appendix for a split-biased version.

>>>>

\subsection{Results and discussion}\label{sec:results}
% \subsection{In-depth comparison of different linkage criteria for \algname{}} 
\textbf{Comparison results } Table \ref{tab:results_cremi_train} shows how \algname{} compares to other tested post-processing methods applied to the predictions of our model. 
% The poor scores achieved by THRESH highlight the difficulty of the task. 
\algname{} with \emph{Average} linkage, representing one of the new algorithms introduced by our generalized framework, significantly outperformed all other previously proposed agglomerative methods like GAEC, Greedy Fixation (using \emph{Sum} linkage) or Mutex Watershed (using \emph{Abs Max} linkage). The remarkably competitive performances of this simple parameter-free agglomerative algorithm are also reported by Table \ref{tab:results_cremi_test} that represents the current leader-board of the challenge: all entries, apart from \algname{}, employ superpixel-based post-processing pipelines, several of which rely on the complex multicut problem. 
In the comparison shown in Table \ref{tab:results_cremi_train}, \algname{} with Average linkage even achieved significantly superior scores compared to other methods based on WSDT superpixels.
Thus, this method offers a simple and successful approach that grow the clusters starting directly from pixels and had the advantage of avoiding potential errors in the superpixel generation. In fact, generating for example good quality WSDT superpixels requires to tune several parameters.   
%Our hypothesis to explain this superior performances is that, currently, there are not good ways of generating superpixels that can take the long-range predictions of the CNN into account. 
%It is of course possible to make use of long-range predictions to compute the edge weights of the superpixel graph, but, in our experience, this process usually involves a lot of parameter tuning and trial and error. 
In Appendix \ref{sec:appendix_exps_full_cremi}, we provide more details about how we scaled up \algname{} to the full datasets and present an extended version of Table \ref{tab:results_cremi_train} including all tested \algname{} algorithms.
Fig. \ref{fig:cremi_comparison} highlights some failure cases of the different agglomerative algorithms included in our framework.

\begin{figure}[t]
        \centering
\begin{minipage}[t]{0.48\textwidth}
% \begin{table}
    \centering
    \scriptsize
    % \begin{subtable}[t!]{0.5\textwidth}\centering
        \begin{tabular}[t]{l|l|c}
        % \toprule
        % & \multicolumn{2}{c}{\thead{Add Cannot-Link Constraints:}} \\
         % & \multicolumn{1}{c}{\thead{\textsc{No}}} & \multicolumn{1}{c}{\thead{\textsc{Yes}}} \\ \midrule
         & \makecell[l]{\algname{}\\ Linkage} & \makecell{Arand-Score \\(higher is better)} \\ \midrule 
         % & \multicolumn{1}{c}{\thead{$\beta$}}  & \thead{AP} & \multicolumn{1}{c}{\thead{$\beta$}} & \thead{AP} \\ \midrule\midrule
\textbf{\algname{}} & \textbf{Average}& \textbf{0.936 $\pm$ 0.004}  \\
Greedy Fixation \cite{levinkov2017comparative} & Sum + Constr. & 0.906 $\pm$ 0.022 \\
DTWS + LMC & -& 0.903 $\pm$ 0.016 \\
DTWS + MC & -& 0.903 $\pm$ 0.017 \\
% DTWS + avgHC &-& \\
% DTWS + MC (SR)& -& 0.900 $\pm$ 0.019 \\
% DTWS + LMC (SR)& -& 0.898 $\pm$ 0.017 \\
Mutex Watershed \cite{wolf2018mutex} & Abs. Max.  & 0.897 $\pm$ 0.012 \\
GAEC \cite{keuper2015efficient} & Sum & 0.872 $\pm$ 0.028 \\
THRESH &-& 0.221  $\pm$ 0.067 \\ 
% DTWS + \algname{} & Average& \TODO{} \\
% DTWS  & -& 0.010 $\pm$ 0.003\\
        \end{tabular}
    \captionof{table}{Arand-Scores achieved by different post-processing methods on CREMI challenge training predictions}
    \label{tab:results_cremi_train}
\end{minipage}\hfill
\begin{minipage}[t]{0.48\textwidth}
    \centering
    \scriptsize
        \begin{tabular}[t]{l|c}
         & \makecell{CREMI Score \\(lower is better)}  \\ \midrule
Our UNet + DTWS + LMC &  \textbf{0.221}\\
PNI-UNet & 0.228 \\
Our UNet + \algname{} Avg-Linkage & 0.241 \\
MALA-UNet + MC \cite{funke2018large} & 0.276 \\
CRUNet \cite{zeng2017deepem3d} & 0.566  \\
LFC \cite{parag2017anisotropic} & 0.616  \\
% Our UNet + DTWS + LMC &  \textbf{0.221} & \textbf{0.108}\\
% PNI-UNet & 0.228 & 0.116 \\
% Our UNet + \algname{} Avg-Linkage & 0.244 & 0.130 \\
% MALA-UNet + MC \cite{funke2018large} & 0.276 & 0.132 \\
% CRUNet \cite{zeng2017deepem3d} & 0.566 & 0.229 \\
% LFC \cite{parag2017anisotropic} & 0.616 & \\
        \end{tabular}
        \vspace*{1.5em}
    \captionof{table}{Current leaderboard of the CREMI challenge}
    \label{tab:results_cremi_test}
\end{minipage}
\end{figure}
\captionsetup[subfigure]{justification=centering, singlelinecheck=off}
\begin{figure}
\centering
    %     \begin{subfigure}[t]{0.49 \textwidth}
    %     \centering
    %     \includegraphics[width=\textwidth,trim=0.55in 0.35in 0.65in 0.80in,clip]{./figs/merge_noise_only_direct.pdf}

@@

\textbf{Noise experiments }  Additionally, we run a set of experiments where the CNN predictions are perturbed by noise, in order to highlight the properties of each \algname{} algorithm and perform an in-depth comparison that is as quantitative as possible. Appendix \ref{sec:appendix_noise_gen} introduces the type of spatially correlated noise that allowed us to perturb the CNN outputs by introducing simulated additional artifacts like missing or false boundary evidences.  
Fig. \ref{fig:noise_plots} summarize our 12000 noise experiments: we focused on the best performing linkage criteria, i.e. \emph{Average}, \emph{Sum} and \emph{Abs Max}, and tested them with different values of noise. %, both with and without use of long-range connections in the grid-graph. % In Fig. \ref{fig:noise_plots}, we used a merge-biased noise decreasing boundary evidence. See Fig. \ref{fig:noise_split} in Appendix for a split-biased version.
